Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-01 chi/piecework/presentation/presentation.tex
weekend updates

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,enumitem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

% Theme colors are derived from these two elements
\setbeamercolor{alerted text}{fg=Orange}
\setsansfont[BoldFont={Source Sans Pro Semibold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmonofont{Source Code Pro}
% \setbeamercolor{frametitle}{bg=stanfordRed}

  % \setbeamercolor*{palette tertiary}{use=structure,fg=stanfordRed,bg=stanfordRed}
% }
% \metroset{set}
\setbeamercolor{institute in head/foot}{fg=stanfordRed}
% \setbeamercolor{progress bar}{fg=stanfordRed}
% \setbeamercolor{progress bar}{bg=gr}
% \setsansfont{Source Sans Pro}

@@

\institute[Stanford]{Stanford University}
\date{\today}

@@

\def\labelitemi{--}

@@

\begin{frame}{Open problems in crowdsourcing}
  \begin{itemize}%[<+- | alert@+>]
    \item \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
                           Nebeling:2016:WCW:2858036.2858169,
                           Hahn:2016:KAB:2858036.2858364}
    \item \textbf{Decomposition}~\textcite{sensitiveTasks,LykourentzouPersonalityMatters,
                              Law:2016:CKC:2858036.2858144,
                              Chang:2016:ACC:2858036.2858411,
                              Newell:2016:OMA:2858036.2858490}
    \item \textbf{Relationships}~\textcite{turkopticon,storiesIraniSilberman,crowdcollab,
                              takingAHITMcInnis}
  \end{itemize}
\end{frame}

@@

\begin{frame}{What does the crowdsourcing literature say?}
    something pretty insightful I bet!
\end{frame}

@@

\begin{frame}[t]\frametitle{Let's compare this stuff}
\framesubtitle{something else}
  \begin{columns}
  \begin{column}{0.5\textwidth}
  % \section*{Piecework}
     some text here some text here some text here some text here some text here

  \end{column}

  \begin{column}{0.5\textwidth}
  % \section*{CrowdWork}
     some text here some text here some text here some text here some text here

  \end{column}
  \end{columns}
\end{frame}

>>>>

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\newenvironment{mystepwiseitemize}{\begin{itemize}[<+-| alert@+>]}{\end{itemize}}
% Theme colors are derived from these two elements
\setbeamercolor{alerted text}{fg=Orange}
\setsansfont[BoldFont={Source Sans Pro Semibold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmonofont{Source Code Pro}
% \setbeamercolor{frametitle}{bg=stanfordRed}

  % \setbeamercolor*{palette tertiary}{use=structure,fg=stanfordRed,bg=stanfordRed}
% }
% \metroset{set}
\setbeamercolor{institute in head/foot}{fg=stanfordRed}
\setbeamercovered{transparent}
\setbeamercovered{again covered={\opaqueness<1->{15}}}
% \setbeamercolor{progress bar}{fg=stanfordRed}
% \setbeamercolor{progress bar}{bg=gr}
% \setsansfont{Source Sans Pro}

@@

\institute[Stanford]{Stanford University}
\date{\today}
\setbeamertemplate{itemize items}{--}

@@

% \def\labelitemi{--}

@@

% \begin{frame}[t]{Open problems in crowdsourcing}
%   \begin{itemize}[<+>]
%     \item \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
%                            Nebeling:2016:WCW:2858036.2858169,
%                            Hahn:2016:KAB:2858036.2858364}
%   \end{itemize}
% \end{frame}

% \begin{frame}[t]{Open problems in crowdsourcing}
%   \begin{itemize}[<+>]
%     \item \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
%                            Nebeling:2016:WCW:2858036.2858169,
%                            Hahn:2016:KAB:2858036.2858364}
%     \item \textbf{Decomposition}~\textcite{sensitiveTasks,LykourentzouPersonalityMatters,
%                               Law:2016:CKC:2858036.2858144,
%                               Chang:2016:ACC:2858036.2858411,
%                               Newell:2016:OMA:2858036.2858490}
%   \end{itemize}
% \end{frame}

\begin{frame}[t]{Open problems in crowdsourcing}
\begin{columns}
\begin{column}{0.6\textwidth}
  \begin{itemize}%[<+>]
    \item<1,4> \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
                           Nebeling:2016:WCW:2858036.2858169,
                           Hahn:2016:KAB:2858036.2858364}
    \item<2> \textbf{Decomposition}~\textcite{sensitiveTasks,LykourentzouPersonalityMatters,
                              Law:2016:CKC:2858036.2858144,
                              Chang:2016:ACC:2858036.2858411,
                              Newell:2016:OMA:2858036.2858490}
    \item<3> \textbf{Relationships}~\textcite{turkopticon,storiesIraniSilberman,crowdcollab,
                              takingAHITMcInnis}

  \end{itemize}

\end{column}
\begin{column}{0.4\textwidth}
test
\end{column}
\end{columns}
%   \begin{figure}[htbp]
%   \centering

% \end{figure}

  % \begin{figure}
  % \includesvg{test}
  % \caption{svg image}
  % \includegraphics<1>[width=.5\textwidth]{figures/handy.png}
  % \includegraphics<2>[width=.5\textwidth]{figures/amt.png}
  % \includegraphics<3>[width=.5\textwidth]{figures/uber.png}
  % \end{figure}
\end{frame}

@@

\begin{frame}{What does the crowdsourcing literature say?}
\begin{columns}[t]

  \begin{column}[t]{0.5\textwidth}
    \begin{itemize}
      \item Build complexity into the process
      \begin{itemize}
        \item Apply CS methods to people~(\textcite{crowdForgeKittur})
      \end{itemize}
    \end{itemize}
  \end{column}

  \begin{column}{0.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/mapReduce.png}
    \end{figure}
  \end{column}

\end{columns}
\end{frame}

@@

\begin{frame}{Comparerereer}
% \framesubtitle{something else}
%   \begin{columns}
%   \begin{column}{0.5\textwidth}
%   % \section*{Piecework}
%      some text here some text here some text here some text here some text here

%   \end{column}

%   \begin{column}{0.5\textwidth}
%   % \section*{CrowdWork}
%      some text here some text here some text here some text here some text here

%   \end{column}
%   \end{columns}
\end{frame}
